---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS_2014_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between gun ownership and race, sex, political views, opinions on capitol punishment and belief in god. The data is from the 2014 general social survey.

I will use the gss data set which has 3842 observations and 1000 variables, as well as the n2014 data set which has 3842 observations and 12 variables to determine the relationship between gun ownership and race, sex, political views, opinions on capitol punishment, and beleif in God. In the gss data set there are 3842 participants with different id numbers who responded in 2014. In the n2014 data set we see their responses according to variables such as gender, education level,and feelings about the bible.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I will use the data from the following charts to analyze the data. 

```{r}
god_table=xtabs(~god + owngun, data=n2014,exclude = "NA")

sex_table=xtabs(~sex + owngun, data=n2014,exclude = "NA")

bible_table=xtabs(~bible + owngun, data=n2014,exclude = "NA")

polviews_table=xtabs(~polviews + owngun, data=n2014,exclude = "NA")

partyid_table=xtabs(~partyid + owngun, data=n2014,exclude = "NA")

cappun_table=xtabs(~cappun + owngun, data=n2014,exclude = "NA")

degree_table=xtabs(~degree + owngun,data=n2014,exclude = "NA")
gss <- tbl_df(gss)
n2014<- select(gss,cappun,owngun,bible,polviews,partyid,region,god,race,owngun,educ,sex,degree)
n2014$cappun <- as_factor(n2014$cappun)
n2014$owngun <- as_factor(n2014$owngun)
n2014$bible <- as_factor(n2014$bible)
n2014$polviews <- as_factor(n2014$polviews)
n2014$partyid <- as_factor(n2014$partyid)
n2014$region <- as_factor(n2014$region)
n2014$god <- as_factor(n2014$god)
n2014$race <- as_factor(n2014$race)
n2014$owngun <- as_factor(n2014$owngun)
n2014$educ <- as_factor(n2014$educ)
n2014$sex <- as_factor(n2014$sex)
n2014$degree <- as_factor(n2014$degree)
n2014 <- mutate(n2014,edlevel=ifelse(educ %in% (0:10),"JRHIGH",ifelse(educ %in% (11:14),"JrCOL",ifelse(educ %in% (15:20),"COLege",NA))))


n2014$partyid <- revalue(n2014$partyid,c(
  "STRONG DEMOCRAT" = "dem",
  "NOT STR DEMOCRAT" = "dem",
  "IND,NEAR DEM"="Indep",
  "IND,NEAR REP"="Indep",
  "INDEPENDENT"="Indep",
  "NOT STR REPUBLICAN"="rep",
  "STRONG REPUBLICAN"="rep",
  "OTHER PARTY"="NA",
    "DK"="NA"
))




```

```{r}
n2014$god <- revalue(n2014$god,c(
  "DONT BELIEVE" = "no",
  "NO WAY TO FIND OUT" = "no",
  "SOME HIGHER POWER" = "maybe",
  "BELIEVE SOMETIMES" = "maybe",
  "BELIEVE BUT DOUBTS" = "maybe",
  "DK" = "maybe",
  "KNOW GOD EXISTS"="yes",
  "IAP"="NA"
))

n2014$owngun <- revalue(n2014$owngun,c(
  "YES" = "YES",
  "NO" = "NO",
  "IAP" = "NA",
  "REFUSED" = "NA",
  "DK" = "NA"
))

n2014$polviews <- revalue(n2014$polviews,c(
  "IAP" = "NA",
  "DK" = "NA",
  "EXTREMELY LIBERAL"="LIBERAL",
  "SLIGHTLY LIBERAL"="LIBERAL",
  "SLGHTLY CONSERVATIVE"="CONSERVATIVE",
  "EXTRMLY CONSERVATIVE"="CONSERVATIVE"
 ))

n2014$cappun <- revalue(n2014$cappun,c(
  "IAP" = "NA",
  "DK" = "NA"))



n2014$bible <- revalue(n2014$bible,c(
  "IAP" = "NA",
  "OTHER" = "NA",
  "DK" = "NA",
  "INSPIRED WORD" = "WORD OF GOD"
))

n2014$race <- revalue(n2014$race,c(
  "IAP" = "NA"))


n2014$degree <- revalue(n2014$degree,c("IAP"="NA",
 "DK" = "NA"))



```
```{r}
race_table=xtabs(~race + owngun, data=n2014,exclude = "NA")
educ_table=xtabs(~edlevel + owngun, data=n2014,exclude = "NA")
god_table=xtabs(~god + owngun, data=n2014,exclude = "NA")

sex_table=xtabs(~sex + owngun, data=n2014,exclude = "NA")

bible_table=xtabs(~bible + owngun, data=n2014,exclude = "NA")

polviews_table=xtabs(~polviews + owngun, data=n2014,exclude = "NA")

partyid_table=xtabs(~partyid + owngun, data=n2014,exclude = "NA")

cappun_table=xtabs(~cappun + owngun, data=n2014,exclude = "NA")

degree_table=xtabs(~degree + owngun,data=n2014,exclude = "NA")

```


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->



#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->




# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
